Towards the near-infrared detection of brown dwarf companions: Exploring methods to detect low mass stellar companions from blended spectra \thanks{Based on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 089.C-0977(A)}

### 2018-08-17 nir_companions.tex
change abstract

% Abstract of the paper
\begin{abstract}
   {\rd{} In this paper we attempt to directly detect the near-infrared spectrum of candidate brown dwarf (BD) companions around FGK stars to assert or discard their stellar nature. We explore two different methods to probe the faint spectra of BD companions. The first technique involves the direct subtraction of two observations shifted to mutually cancel out the spectra of the host star. The second technique applies a \(\chi^{2}\) fit to the individual observations of a synthetic binary model comprised of two PHOENIX-ACES spectra. The observed spectra are wavelength calibrated and corrected for the atmospheric absorption with the aid of synthetic telluric models. The direct subtraction method failed to detect the signature of the companions due to poor observational constraints (the observations were insufficiently separated in radial velocity). The \(\chi^{2}\) technique developed here is able to fit the component for the host star but unable to successfully detect the faint spectra of even the largest companion in our sample. We explore how the companion recovery fitting performs on simulated observations and discuss reasons for the non-detection observed. From the injection-recovery analysis, this technique in its current form, is insufficient to recover a companion below 3800~K which corresponds to an upper mass limit for the companions around \(\rm 600~M_{Jup}\). This work highlights the challenges in the spectral detection of faint companions. We explore the limitations of the direct subtraction method in the case of small RV separation, and companion detection with synthetic models at low companion/host flux ratios below 1 per cent, made difficult by the discrepancy between observed and synthetic spectra around 2100~nm.}
\end{abstract}

>>>>

% Abstract of the paper
\begin{abstract}
   {In this paper we attempt to directly detect the near-infrared spectrum of candidate brown dwarf (BD) companions around FGK stars to assert or discard their stellar nature. We explore two different methods to probe the faint spectra of BD companions. The first technique involves the direct subtraction of two observations shifted to mutually cancel out the spectra of the host star. The second technique applies a \(\chi^{2}\) fit to the individual observations of a synthetic binary model comprised of two PHOENIX-ACES spectra. The observed spectra are wavelength calibrated and corrected for the atmospheric absorption with the aid of synthetic telluric models. The direct subtraction method failed to detect the signature of the companions due to poor observational constraints (the observations were insufficiently separated in radial velocity). The \(\chi^{2}\) technique is unable to successfully detect the faint spectra of even the largest companion in our sample. We explore how the companion recovery fitting performs on simulated observations and discuss reasons for the non-detection observed. From the injection-recovery analysis, this technique in its current form, is insufficient to recover a companion below 3800~K which corresponds to an upper mass limit for the companions around \(\rm 600~M_{Jup}\). This work highlights the challenges in the spectral detection of faint companions. We explore the limitations of the direct subtraction method in the case of small RV separation, and companion detection with synthetic models at low companion/host flux ratios below 1 per cent, made difficult by the discrepancy between observed and synthetic spectra around 2100~nm.}
\end{abstract}
